High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns

### 2021-08-11 paper/main.tex
updates from editor

In brief, we computed timeseries of dynamic high-order correlations
that were similar across participants in each of two randomly assigned
groups: a training group and a test group.  We then trained
classifiers on the training group's data to match each sample from the
test group with a stimulus timepoint.  Each classifier comprised a
weighted blend of neural patterns that reflected up to
$n^\mathrm{th}$-order dynamic correlations (see Feature
  weighting and testing, Fig.~\ref{fig:pipeline}).  We repeated this process for
$n \in \left\{ 0, 1, 2, ..., 10 \right\}$.  Our examinations of
synthetic data suggested that none of the kernels we examined were
``universal'' in the sense of optimally recovering underlying
correlations regardless of the temporal structure of those
correlations.  We found a similar pattern in the (real) fMRI data,
whereby different kernels yielded different decoding accuracies, but
no single kernel emerged as the clear ``best.''  In our analyses of
neural data, we therefore averaged our decoding results over a variety
of kernel shapes and widths in order to identify results that were
robust to specific kernel parameters (see Identifying robust
  decoding results).

@@

The authors declare that the data supporting the findings of this
study as well as the source data for this paper are available at
\href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.4}{github.com/ContextLab/timecorr-paper/releases/tag/v0.4}
and has been deposited in the Zenodo database under accession code \href{https://doi.org/10.5281/zenodo.5165253}{https://doi.org/10.5281/zenodo.5165253}.
The raw fMRI data are protected and are not available due to data
privacy laws. The processed fMRI dataset collected by
\cite{SimoEtal16} has been made publicly available \cite{SimoEtal16b} at
\href{http://arks.princeton.edu/ark:/88435/dsp015d86p269k}{arks.princeton.edu/ark:/88435/dsp015d86p269k}.

@@

\section*{Competing interests}
The authors declare no competing financial interests.

>>>>

In brief, we computed timeseries of dynamic high-order correlations
that were similar across participants in each of two randomly assigned
groups: a training group and a test group.  We then trained
classifiers on the training group's data to match each sample from the
test group with a stimulus timepoint.  Each classifier comprised a
weighted blend of neural patterns that reflected up to
$n^\mathrm{th}$-order dynamic correlations (see Feature
  weighting and testing).  We repeated this process for
$n \in \left\{ 0, 1, 2, ..., 10 \right\}$.  Our examinations of
synthetic data suggested that none of the kernels we examined were
``universal'' in the sense of optimally recovering underlying
correlations regardless of the temporal structure of those
correlations.  We found a similar pattern in the (real) fMRI data,
whereby different kernels yielded different decoding accuracies, but
no single kernel emerged as the clear ``best.''  In our analyses of
neural data, we therefore averaged our decoding results over a variety
of kernel shapes and widths in order to identify results that were
robust to specific kernel parameters (see Identifying robust
  decoding results).

@@

The authors declare that the data supporting the findings of this
study as well as the source data for this paper are available at
\href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.4}{github.com/ContextLab/timecorr-paper/releases/tag/v0.4}
and has been deposited in the Zenodo database under accession code
\href{https://doi.org/10.5281/zenodo.5165253}{https://doi.org/10.5281/zenodo.5165253}.
The source data underlying Figs. 2-6 and Supplementary Figs. S1-S9 are
provided as a Source Data file. Source Data are provided with the
manuscript. The raw fMRI data are protected and are not available due to data
privacy laws. The processed fMRI dataset collected by
\cite{SimoEtal16} has been made publicly available \cite{SimoEtal16b} at
\href{http://arks.princeton.edu/ark:/88435/dsp015d86p269k}{arks.princeton.edu/ark:/88435/dsp015d86p269k}.

@@

\section*{Competing interests}
The authors declare no competing interests.
